### 2018-04-06 Paper/sense.tex
...

\noindent The NPT stage of the simulation was allowed to continue for a sufficiently long duration to ensure
that the system is relaxed to a steady value of the bar length as shown in Figure~\ref{fig:dgsm1}(b).

>>>>

\noindent The NPT stage of the simulation was allowed to continue for a sufficiently long duration to ensure
that the system is relaxed to a steady value of the bar length as shown in Figure~\ref{fig:dgsm1}(b).
The following algorithm provides the sequence of steps that were used to obtain approximate estimates of the
sensitivity measures for the SW potential parameters:
\bigskip

\texttt{Algorithm}

\begin{algorithm}[H]
\SetAlgoLined
%\nonl \scriptsize{\textsc{Part I: Parameter Screening}}
%\nonl \textbf{\texttt{Algorithm}}\;
\texttt{Generate $n_1$ points in $\mathbb{R}^{d}$}\;
\texttt{Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points}
\texttt{\color{blue} $\%$~$d$: Number of parameters in the SW potential i.e. 7}\;
\texttt{Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}}\;
\texttt{Determine initial ranks, $\mathcal{R}^{old}$ of the parameters based on $\hat{\mathcal{C}_i\mu_i}$ values}\;
\texttt{set $k$ = 1}
\texttt{\color{blue}$\%$~$k$:~Iteration counter}\;
\Repeat{\texttt{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ $\&$ 
$max\_pdev$~$>\tau$)~\color{blue}$\%$~$\tau$:~Tolerance}}{
\texttt{Generate $n_k$ new points in $\mathbb{R}^{d}$}\;
\texttt{Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points}\;
\texttt{Compute and store model evaluations at the $n_k(d+1)$ points}\;
\texttt{Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points}\;
\texttt{Determine new ranks, $\mathcal{R}^{new}$ based on updated $\hat{\mathcal{C}_i\mu_i}$ values}\;
\texttt{Compute $max\_pdev$ = max($\frac{|\mu_{i,k} - \mu_{i,k-1}|}{ \mu_{i,k-1}}$)}
\texttt{\color{blue}$\%$~$max\_pdev$: Maximum percentage deviation in $\mu_i$ between successive iterations.}\;
\texttt{set $k$ = $k$ + 1}\;
}
\end{algorithm}

For the present application, we begin with $n_1$ = 10 samples in the 7D parameter space and add 5 points
at each iteration. Using a tolerance, $\tau$ = 0.05, the above algorithm took 4 iterations i.e. 25 points to 
provide approximate estimates for $\mu_i$. Since finite difference was used to estimate the derivates in
Eq.~\ref{eq:mu}, it required 25(7+1) i.e. 200 MD runs. It must be noted that although the computational effort
pertaining to the estimation of DGSM can be substantial it is nevertheless several orders of magnitude smaller
than directly estimating the Sobol indices as mentioned earlier. 
In Figure~\ref{fig:screen}, we plot $\hat{\mathcal{C}_i\mu_i}$ as obtained for the SW parameters at the 
end of 4 iterations. It appears that $\gamma$ is significantly more important that the rest, whereas NEMD
predictions are not so sensitive to $B$ and $p$. Large sensitivity towards $\gamma$ and $\alpha$ (cut-off radius)
 is in fact expected since  these two parameters impact the lattice constant directly.
